DRAFT

### 2022-11-02 Draft.Rmd
Update Draft.Rmd

### • Distance
### 75% of the hotels are located between 0 and 2.4 miles from the main city center. 
The histogram below shows the distribution of the distances from the city center, the limit for x-axis was set at 25 miles.
```{r echo=FALSE}
ggplot(data=df2, aes(x=distance)) + geom_histogram(fill='navyblue', color='white', bins = 35) + 
  labs(x='Distance', y='Count')
```

@@

### • Trueprice
### 99% of the prices are below 600 EUR, thus, the limit for x-axis in histogram was set to this value.
### The distribution of the prices is skewed to the right, therefore, we can conclude that the mean price is greater then the mode.
```{r echo=FALSE, message=FALSE}
ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
  labs(x='Price', y='Count') + xlim(0, 1200) 
```
### • Year and month
```{r echo=FALSE}
kable(count(df2, year))
```
```{r echo=FALSE}
kable(count(df2, month))
```
### • Accommodation type
```{r echo=FALSE}
kable(count(df2,acctype_f) %>% arrange(desc(n)))
```

@@

## Findings
### • Mean prices for countries
```{r}
datasummary(trueprice*addresscountryname ~ Mean + Max + Min, data=df2)
```

### • Ratings for diff countries
```{r}
datasummary(actualrating*addresscountryname ~ Mean, data=df2)
```

>>>>

### • Distance
### 75% of the hotels are located between 0 and 2.4 miles from the main city center. 
### The histogram below shows the distribution of the distances from the city center, the limit for x-axis was set at 25 miles.
```{r echo=FALSE}
ggplot(data=df2, aes(x=distance)) + geom_histogram(fill='navyblue', color='white', bins = 35) + 
  labs(x='Distance', y='Count')
```

@@

### • Trueprice
### 99% of the prices are below 600 EUR, thus, the limit for x-axis in histogram was set to this value.
### The distribution of the prices is skewed to the right, therefore, we can conclude that the mean price is greater then the mode.
```{r echo=FALSE, message=FALSE}
ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
  labs(x='Price', y='Count') + xlim(0, 1200) 
```

### • Year and month
```{r echo=FALSE}
kable(count(df2, year))
```
```{r echo=FALSE}
kable(count(df2, month))
```
### • Accommodation type
```{r echo=FALSE}
kable(count(df2,acctype_f) %>% arrange(desc(n)))
```

@@

## 1.3 Findings
### • Mean prices for countries
```{r echo=FALSE}
datasummary(trueprice*addresscountryname ~ Mean + Max + Min, data=df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```
